---
title: "Diamonds"
author: "Beroy Jenkins"
date: "26/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages('ggplot2', dependencies = T) 
library(ggplot2)
```



```{r}
data("diamonds")
summary(diamonds$cut[2])

?diamonds
str(diamonds)
```

```{r}
ggplot(aes(x = price), data = diamonds)+
  geom_histogram(binwidth = 1)
  
  
qplot(data = diamonds, x =  price)


```{r}+
diamonds$price[names(diamonds$price)>500]

as.data.frame(table(diamonds$price >= 15000))
```

```{r}
by(diamonds$price, diamonds$cut, summary)
```

```{r}
ggplot(aes(x = price/carat), data = diamonds)+
  geom_histogram()+
  scale_x_log10()+
  facet_wrap(~cut, scales = "free_y")
```


```{r}
ggplot(aes(x = color, y = price), data = diamonds)+
  geom_boxplot()+
  coord_cartesian(ylim =c(0, 8750))
```


```{r}
by(diamonds$price,diamonds$color,summary)

IQR(subset(diamonds, color =='D')$price)
IQR(subset(diamonds, color == "J")$price) 

```

```{r}
ggplot(aes(x = color, y= price/carat), data = diamonds)+
  geom_boxplot()
```

```{r}
ggplot(aes(x = carat), data = diamonds) +
  geom_freqpoly(aes(color = carat),binwidth = 0.1) + 
  scale_x_continuous(breaks = seq(0,3,0.2)) + 
  scale_y_continuous(breaks=seq(0,16000,2000))+
  xlab('carat')

table(diamonds$carat)

```

